\bf\mftitle

### 2011-02-23 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}, where rectangles represent folders and rounded rectangles files. Folder in filesystem is considered as jInfer project folder, if contains \emph{jinferproject} subfolder. These folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is xml file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}).

@@

\code{InputFiles} is utility class that stores/loads input file paths into/from input.files xml file. For this purpose, class uses \emph{JAXB} architecture to unmarshall/marshall xml file into/from java content objects. Xml structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{xml}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

@@

>>>>

With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}, where rectangles represent folders and rounded rectangles files. Folder in filesystem is considered as jInfer project folder, if contains \emph{jinferproject} subfolder. This folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is xml file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}). \emph{Output} subfolder contains schema files which were generated by jInfer inference.

@@

\code{InputFiles} is utility class that stores/loads input file paths into/from input.files xml file. For this purpose, class uses \emph{JAXB} \cite{JAXB} architecture to unmarshall/marshall xml file into/from java content objects. Xml structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{xml}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

@@

\begin{figure}
	\centering\includegraphics[scale=\myscale]{node_structure}
	\caption{Project directory structure} \label{node-structure}
\end{figure}

Each project in NBP is after creation opened in project window and has some visual tree structure where each node in this tree is represented by NBP \code{Node} class. This structure is in jInfer project type provided by \code{JInferLogicalView} class that implements \code{LogicalViewProvider} interface from NBP and is available through \code{JInferProject} lookup. This class has one important method, \code{createLogicalView()} that returns instance of \code{RootNode} class of root node. Simple class structure is described in figure \ref{node-structure}.\\

\code{RootNode} extends NBP \code{AbstractNode} class which is basic implementation of NBP \code{Node}. This node contains four children nodes: three for input files (Document, Schema and Query) and one for output files generated by inference (Output). Root node also offers actions for adding input files, run inference and standard project actions like delete or move/rename project.\\

Each of the \emph{input} nodes is represented by \code{FolderNode} class and contains \emph{input file} nodes (represented by \code{FileNode} class) representing files added to the jInfer project. Notice that these \emph{input file} nodes represents files from filesystem and are not copied to project folder structure. Because of this, if you delete this nodes from project tree, files from filesystem are not deleted.\\

\code{OutputNode} class represents \emph{Output} node in jInfer project type tree and is slightly different from \emph{input} nodes, because it refers to \emph{output} subfolder in project filesystem hierarchy. In other words, files contained in this folder are shown as subnodes in \emph{Output} node in project tree. This subnodes are represented by \code{OutputFileNode} class. Unlike \emph{input file} nodes, if you delete \emph{output file} node under the \emph{Output} node, file represented by this node is also deleted from filesystem.
